Preliminary Insights into Indigenous Subsistence and Colonial Encounters: A Zooarchaeological Perspective from Kiwulan in Northeastern Taiwan

### 2025-03-12 analysis/paper/paper.qmd
organized code

# get the bone mineral desity data
deer_element_BMD <- readr::read_csv(here::here("analysis", "data", "derived_data", "deer_BMD.csv"))
cor_sur_BMD <- cor.test(deer_element_BMD$NISP, deer_element_BMD$BMD)
survivor_cor <- round(c(cor_sur_BMD$estimate, cor_sur_BMD$p.value),2)

@@

```{r}
#| label: fig-deer-portion
#| echo: false
#| fig-cap: "A: The frequency of deer skeletal parts using NISP across cultural layers at Kiwulan. B: Bone minerial density agaist %survivorship of deer remains."

>>>>

# get the bone mineral density data
deer_element_BMD <- readr::read_csv(here::here("analysis", "data", "derived_data", "deer_BMD.csv"))
cor_sur_BMD <- cor.test(deer_element_BMD$NISP, deer_element_BMD$BMD)
survivor_cor <- round(c(cor_sur_BMD$estimate, cor_sur_BMD$p.value),2)

@@

```{r}
#| label: fig-deer-portion
#| echo: false
#| fig-cap: "A: The frequency of deer skeletal parts using NISP across cultural layers at Kiwulan. B: Bone mineral density against %survivorship of deer remains."
